Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-11-01 MHCpaper/MHCsupp.tex
added chr2 fig

We find that
%
\begin{equation}\label{eq:binaryflux}
  \Phi = \frac{q\pot q\dep \Delta f}{\lambda}, \qquad
  \pdiff{\Phi}{q\dep} = \frac{f\pot (q\pot)^2 \Delta f}{\lambda^2}, \qquad
  \pdiff{\Phi}{f\pot} = \frac{q\pot q\dep \lambda\inc}{\lambda^2}.
\end{equation}
%
The flux is a monotonically increasing function of $q\dep$ and $f\pot$.
Therefore, enhancing plasticity in this way or pre-training can only enhance the initial learning rate for all values of the parameters, unlike the experimental results shown in \modelfig.

@@

First, consider the wild-type.
Without pre-training:
%
\begin{equation}\label{eq:binWTnopre}
  \Phi = {\Delta f}\, q.
\end{equation}
%
With pre-training:
%
\begin{equation}\label{eq:binWTpre}
\begin{aligned}
  \Phi &= 2{\Delta f}\, q.
\end{aligned}
\end{equation}
%
So, we see that pre-training will speed up learning for all parameter values, unlike what is seen in the experiment.
This can be seen in
\autoref{fig:sim_results}\ref{fig:binary_sim} %\autoref{fig:binary}\ref{fig:binary_learnS}
(black curves).

@@

\bibliographystyle{utcaps_sl}
\bibliography{maths,neuro,markov}

>>>>

We find that
%
\begin{equation}\label{eq:binaryflux}
  \Phi = \frac{q\pot q\dep \Delta f}{\lambda}, \qquad
  \pdiff{\Phi}{q\dep} = \frac{f\pot (q\pot)^2 \Delta f}{\lambda^2}, \qquad
  \pdiff{\Phi}{f\pot} = \frac{q\pot q\dep \lambda\inc}{\lambda^2}.
\end{equation}
%
The flux is a monotonically increasing function of $q\dep$ and $f\pot$.
Therefore, enhancing plasticity in this way, or pre-training, can only enhance the initial learning rate for all values of the parameters, unlike the experimental results shown in \modelfig.

@@

First, consider the wild-type.
Without pre-training:
%
\begin{equation}\label{eq:binWTnopre}
  \Phi = {\Delta f}\, q.
\end{equation}
%
With pre-training:
%
\begin{equation}\label{eq:binWTpre}
\begin{aligned}
  \Phi &= 2{\Delta f}\, q.
\end{aligned}
\end{equation}
%
So, we see that pre-training will speed up learning, unlike what is seen in the experiment.
This can be seen in
\autoref{fig:sim_results}\ref{fig:binary_sim} %\autoref{fig:binary}\ref{fig:binary_learnS}
(black curves).

@@

\section{Model of non-specific CF stimulation}\label{sec:chr2}

\begin{figure}[p]
\begin{myenuma}
  \begin{tabular}{lll}
      \item\label{fig:seial_ChR2}
      \aligntop{\includegraphics[width=0.24\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_ChR2}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.12\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_ChR2}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate.svg}}
      \\[1.3cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{serial_fit_ChR2_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{binary_ChR2_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{multistate_lin_ChR2_learnS.eps}}
      \\[4.5cm]
      \item\label{fig:pooled_ChR2}
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_ChR2}
      \aligntop{\includegraphics[width=0.24\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_ChR2}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate_nonuni.svg}}
      \\[1.8cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly_ChR2_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{cascade_fit_ChR2_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{nonuni_fit_ChR2_learnS.eps}}
  \end{tabular}

  \vspace{0.5cm}
  \item\label{tab:params_ChR2}\aligntop{
  \begin{tabular}{|l|c|c|c|c|c|c|c|}
    \cline{1-8}
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \#  & \multicolumn{2}{c|}{Plasticity param.} & \multicolumn{3}{c|}{$f\dep$} & $r\tpre$ \\
    \cline{3-7}
    & states & pot & dep & base & inc & CF Stim & {} \\

    \cline{1-8}
    Serial       & 10 & $0.12$  & $0.14$        & 0.5   & 0.89 & 0.9879 & 100 \\
    Two-state    & 2  & $0.1$   & $0.4$         & 0.5   & 0.7  & 0.91   & 5   \\
    Multistate   & 10 & $0.3$   & $0.3$         & 0.5   & 0.8  & 0.96   & 5   \\
    Pooled res.\ & 7  & $0.08$  & $[0.006,0.6]$ & 0.5   & 0.9  & 0.99   & 20  \\
    Cascade      & 14 & $0.386$ & $0.398$       & 0.522 & 0.63 & 0.99   & 200  \\ 
    Non-uni.\    & 12 & $0.4$   & $0.4$         & 0.5   & 0.7  & 0.99   & 500  \\
    \cline{1-8}
  \end{tabular}}
  \end{myenuma}
  \caption[Simulation results for various models]{(\ref{fig:seial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (black) and after non-specific CF stimulation (cyan) for wild-type models.
  (\ref{tab:params}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_ChR2}
\end{figure}

\bibliographystyle{utcaps_sl}
\bibliography{neuro,markov}
